Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-25 draft.tex
tiny changes

Pick any alternative $c$ that is not $a$ or $b$. 
%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$. Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$. Define $a_t$ similarly, for the alternative $a$. By construction, $a_r = q$, $a_{r+2} = q+p = a_m$. 
Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly. Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$. To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$. By our construction, the two times $\delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights. Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$. Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$). Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).

>>>>

Pick any alternative $c$ that is not $a$ or $b$. 
%Let $c_t$ denote the number of times $c$ reaches rank $t$ or better in $P$. Note that $c_m = p+q$ and $c_t ≤ p + q, 1 ≤ t ≤ m$. Define $a_t$ similarly, for the alternative $a$. By construction, $a_r = q$, $a_{r+2} = q+p = a_m$. 
Define $c'_t$ as the number of times $c$ gets rank $t$ or better in $P'$, and define $a'_t$ similarly. Now $a'_1 ≥ \delta, a'_t ≥ 2\delta \text{ for } 2 ≤ t < m, a'_{r+2} = q+p+2\delta = a'_m$. To obtain upper bounds for $c'_t$, assume $c$ is ranked first by the $p+q$ agents voting in profile $P$. By our construction, the  $2 \delta$ new agents of $P'$ give to $c$ the ranks $(3, m)$, or $(4, m-1)$, … Observe that the score of $c$ is maximal for attribution $(3, m)$, by convexity of the weights. Therefore, in the best case for $c$, $c'_1 ≤ p + q, c'_2 ≤ p+q, c'_t ≤ p+q+\delta \text{ for } 3 ≤ t < m, c'_m ≤ p+q+2\delta$. Observe that $a'_t ≥ c'_t, 1 ≤ t ≤ m$ (with strict inequality for $t=2$). Because weights are non increasing, this guarantees, with $\delta = p + q$, that the score of $a$ is not lower than the one of $c$ (it is even strictly higher, thanks to the strict inequality).
